GM12878 Deamination Anchored Excision Site Figure Generation

### 2022-06-14 R/GM12878DeaminationAnchoredExcisionSiteDataGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

expansionOffset = 10
cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

@@

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
                             rep2 = CisplatinTimepoints)
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
      repitition = names(CisplatinMismatchData)[i], expansionNum = expansionOffset, filtering = filtering
      ))
  }
}
```

```{r generate_simplified_and_filtered_mismatch_data}
# Filter the reads by length and mismatch type (single C>T).
CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = minReadLength, maxReadLength = maxReadLength)
))

# Simplify the data
CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
))

# Read mismatch frequency z-scores.
# NOTE: Using NHF1 CPD scores. Otherwise, data will be too tightly constrained.
NHF1CPDMMFreqZScores = fread(generateFilePath(
      directory = NHF1DeaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = "NHF1", lesion = "CPD", repitition = "rep1",
      timepoint = "1h", filtering = filtering, includedMismatches = c("C>T")
))

# Further filter data by read position based on length
CisplatinMismatchData = lapply(CisplatinMismatchData, function(CisplatinMismatchDataRep) {
  lapply(CisplatinMismatchDataRep, filterMismatchesByPositionAndReadLength,
         NHF1CPDMMFreqZScores, expansionOffset = expansionOffset)
})
```

```{r orient_data_to_mismatch_positions}
# NOTE: The assignment to null is there so that the garbage collector can free up memory, and
#       I can still switch to new variable names for organizational purposes.
threePrimeMismatchAnchoredCisplatinData = lapply(CisplatinMismatchData, function(x) {
  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
})
fivePrimeMismatchAnchoredCisplatinData = lapply(CisplatinMismatchData, function(x) {
  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
})
CisplatinMismatchData = NULL
```

>>>>

expansionOffset = 10
cellType = "GM12878"
cisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

@@

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], expansionNum = expansionOffset, filtering = filtering
      ))
  }
}
```

```{r generate_simplified_and_filtered_mismatch_data}
# Filter the reads by length and mismatch type (single C>T).
cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = minReadLength, maxReadLength = maxReadLength)
))

# Simplify the data
cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
))

# Read mismatch frequency z-scores.
cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}

# Further filter data by read position based on length
cisplatinMismatchData = mapply(function(cisplatinMismatchDataRep, cisplatinMMFreqZScoreRep) mapply(
  filterMismatchesByPositionAndReadLength, cisplatinMismatchDataRep, cisplatinMMFreqZScoreRep,
  expansionOffset = expansionOffset, SIMPLIFY = FALSE
), cisplatinMismatchData, cisplatinMMFreqZScores, SIMPLIFY = FALSE)
```

```{r orient_data_to_mismatch_positions}
# NOTE: The assignment to null is there so that the garbage collector can free up memory, and
#       I can still switch to new variable names for organizational purposes.
threePrimeMismatchAnchoredCisplatinData = lapply(cisplatinMismatchData, function(x) {
  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
})
fivePrimeMismatchAnchoredCisplatinData = lapply(cisplatinMismatchData, function(x) {
  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
})
cisplatinMismatchData = NULL
```

### 2022-06-14 R/GM12878DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

expansionOffset = 10
cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  threePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fivePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}
```

```{r cisplatin_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r cisplatin_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r read_sequence_enrichment_data}
threePrimeMMAnchoredCisplatinEnrichment = list(rep1 = CisplatinTimepoints,
                                               rep2 = CisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinEnrichment[[i]])) {
    threePrimeMMAnchoredCisplatinEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCisplatinEnrichment = list(rep1 = CisplatinTimepoints,
                                              rep2 = CisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinEnrichment[[i]])) {
    fivePrimeMMAnchoredCisplatinEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r cisplatin_sequence_enrichment, fig.width = 11, fig.height = 9}
plotSequenceEnrichment(threePrimeMMAnchoredCisplatinEnrichment$rep1,
                       title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredCisplatinEnrichment$rep2,
                       title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredCisplatinEnrichment$rep1,
                       title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredCisplatinEnrichment$rep2,
                       title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
```

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = CisplatinTimepoints,
                                            rep2 = CisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = CisplatinTimepoints,
                                           rep2 = CisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 9}
plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep1,
                        title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep2,
                        title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))

plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep1,
                        title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep2,
                        title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
```

>>>>

expansionOffset = 10
cellType = "GM12878"
cisplatinTimepoints = list(`90min` = NULL)
repNames = c("rep1", "rep2", "all_reps")
minReadLength = 22; maxReadLength = 30

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  threePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fivePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}
```

```{r cisplatin_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq[[i]], 
                                 title = paste(c("cisplatin", titleCaseFiltering,
                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                 secondaryYAxisLabel = "5' Cut Site Distance",
                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
}

for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq[[i]], 
                                 title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
}
```

```{r cisplatin_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq[[i]], 
                                 title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
}

for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq[[i]], 
                                 title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
}
```

```{r read_sequence_enrichment_data}
threePrimeMMAnchoredCisplatinEnrichment = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinEnrichment[[i]])) {
    threePrimeMMAnchoredCisplatinEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCisplatinEnrichment = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinEnrichment[[i]])) {
    fivePrimeMMAnchoredCisplatinEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r cisplatin_sequence_enrichment, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMMAnchoredCisplatinEnrichment)) {
  plotSequenceEnrichment(threePrimeMMAnchoredCisplatinEnrichment[[i]],
                         title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Enrichment", repNames[i]), collapse = ' '),
                         secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                         expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
}

for (i in seq_along(fivePrimeMMAnchoredCisplatinEnrichment)) {
  plotSequenceEnrichment(fivePrimeMMAnchoredCisplatinEnrichment[[i]],
                         title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Enrichment", repNames[i]), collapse = ' '),
                         secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                         expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
}
```

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 9}
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq[[i]],
                          title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
}

for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq[[i]],
                          title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
}
```
